---
title: "Introduction to NRRR package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_to_NRRR_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This document provides a brief introduction to the functions of implementing nested reduced-rank regression (NRRR) from how to generate functional observations with user-provided model dimensions to how to predict response trajectories based on the fitting results. Both the nested reduced-rank regression and the nested reduced-rank ridge regression fitting procedures are displayed. For an introduction of the NRRR model and its application in an electricity data analysis, please see another vignette **Adelaide Electricity Demand Data Analysis with NRRR**. 

## Install the package
```{r setup}
#install.packages("devtools")
#devtools::install_github("xliu-stat/NRRR")
library(NRRR)
set.seed(1)
```

# Nested reduced-rank regression
### Generate data
```{r}
# dimension
n <- 100
p <- 10
d <- 10

# functional setting
ns <- 60
nt <- 60
jx <- 8
jy <- 8

# true model size
r <- 5
rx <- 3
ry <- 3

# signal and noise setting
s2n <- 1
rho_X <- 0.1
rho_E <- 0
Sigma <- "CorrAR"

# generate data
mydata <- nrrr.sim(n, ns, nt, r, rx, ry, jx, jy, p, d,
                   s2n, rho_X, rho_E, Sigma)
Y <- mydata$Yest
X <- mydata$Xest
```

## Nested reduced-rank regression
### BIC rank selection
```{r}
# BIC tuning
fit_nrrr1 <- NestRRR.select(Y, X, NULL, NULL, jx, jy, p, d, n, 
                            maxiter = 300, conv = 1e-2,
                            quietly = TRUE, method = 'RRR', ic = "BIC")
fit_nrrr1$rank
fit_nrrr1$rx
fit_nrrr1$ry
```

### Cross-Validation rank selection
```{r}
# CV tuning
fit_nrrr2 <- NestRRR.cv.select(Y, X, nfold = 10, norder = NULL, NULL, NULL,
                          jx, jy, p, d, n, maxiter = 300, conv = 1e-2, 
                          quietly = TRUE, method = 'RRR')
fit_nrrr2$rank
fit_nrrr2$rx
fit_nrrr2$ry
```


## Nested reduced-rank ridge regression
We first obtain a reference tuning level from a cross validation tuned reduced-rank ridge regression:
```{r}
# Reduced-rank ridge regression
xr <- sum(svd(X)$d > 1e-2)
rankmax <- min(xr, d * jy, 20) 
fit_rrs <- RRRR.cv(Y, X, rankmax = rankmax, nfold = 10, nlam = 20, 
                   lambda = seq(0, 1, length = 20), norder = NULL)
lambda <- fit_rrs$lam
```

### BIC rank selection
```{r}
fit_nrrs1 <- NestRRR.select(Y, X, NULL, NULL, jx, jy, p, d, n, 
                            maxiter = 300, conv = 1e-2,
                            quietly = TRUE, method = 'RRS', 
                            lambda = lambda)
fit_nrrs1$rank
fit_nrrs1$rx
fit_nrrs1$ry
```

### Cross-Validation rank selection
```{r}
fit_nrrs2 <- NestRRR.cv.select(Y, X, nfold = 10, norder = NULL,
                               NULL, NULL, jx, jy, p, d, n,
                               maxiter = 300, conv = 1e-2, quietly = TRUE, 
                               method = 'RRS', lambda = lambda)
fit_nrrs2$rank
fit_nrrs2$rx
fit_nrrs2$ry
```


# Prediction
```{r}
Ypred_nrrr <- NestRRR.prediction(mydata$tseq, mydata$X, mydata$sseq,
                                 fit_nrrr1$Ag, fit_nrrr1$Bg, fit_nrrr1$Al, 
                                 fit_nrrr1$Bl, mydata$phi)
```

